---
title: "Group Research Proposal"
subtitle: "World Happiness Report"
author: "Aidan, Hrissy, Jack, Keyu"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(janitor)
library(readxl)
DataForTable2_1 <- read_excel("DataForTable2.1.xls") %>%
clean_names()
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/confetti.jpg"
)
```

class: center, middle

## What is correlation between Life Expectancy and Overall Happiness in the World?

---

class: inverse, center, middle

# Section title

---

# Hello World

- Click the `Knit` button to compile your presentation

- Make sure to commit and push all resulting files to your GitHub repo

---

class: inverse, middle, center

# Using xaringan

---

# xaringan

- The presentation is created using the `xaringan` package

- Use `---` to separate slides and `--` for incremental builds

--

- Like this

---

# Layouts

You can use plain text

- or bullet points

.pull-left[
or text in two columns $^*$
]
.pull-right[
- like
- this
]

.footnote[
[*] And add footnotes
]

---

# Code

```{r boring-analysis}
# a boring analysis
ave <- mean(cars$dist)
print(ave)
```

---

# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
iris_modified <- iris %>%
  mutate(Species = fct_other(Species, keep = "setosa"))
```

```{r plot-iris, echo = FALSE}
DataForTable2_1 %>%
  filter(
    year == 2021,
    healthy_life_expectancy_at_birth != "NA",
    life_ladder != "NA"
  ) %>%
  ggplot(aes(x = healthy_life_expectancy_at_birth, y = life_ladder)) +
  geom_point() +
  geom_smooth(
    formula = y ~ x,
    method = lm
  ) +
  ggpubr::stat_regline_equation(
    formula = y ~ x,
    show.legend = FALSE
  )

```

---

## Plot and text

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r DataForTable2_1-table, echo = FALSE}

DataForTable2_1 %>%
  select(country_name, year, life_ladder, healthy_life_expectancy_at_birth, social_support) %>%
  filter(year == "2011" & healthy_life_expectancy_at_birth != "NA" & social_support != "NA") %>%
  summarise(
            min_happiness = min(life_ladder),
            max_happiness = max(life_ladder),
            avg_happiness = mean(life_ladder),
            min_life_expectancy = min(healthy_life_expectancy_at_birth),
            max_life_expectancy = max(healthy_life_expectancy_at_birth),
            avg_life_expectancy = mean(healthy_life_expectancy_at_birth),
            min_social_support = min(social_support),
            max_social_support = max(social_support),
            avg_social_support = mean(social_support))

DataForTable2_1 %>%
  select(country_name, year, life_ladder, healthy_life_expectancy_at_birth, social_support) %>%
  filter(year == "2021" & healthy_life_expectancy_at_birth != "NA" & social_support != "NA") %>%
  summarise(
            min_happiness = min(life_ladder),
            max_happiness = max(life_ladder),
            avg_happiness = mean(life_ladder),
            min_life_expectancy = min(healthy_life_expectancy_at_birth),
            max_life_expectancy = max(healthy_life_expectancy_at_birth),
            avg_life_expectancy = mean(healthy_life_expectancy_at_birth),
            min_social_support = min(social_support),
            max_social_support = max(social_support),
            avg_social_support = mean(social_support))

```
      Min Happiness  Max Happiness  Avg Happiness 
2011      2.936          7.788           5.420
2021      2.179          7.794           5.623

      Min Life Expectancy   Max Life Expectancy   Avg Life Expectancy
2011      33.32                   73.12                61.96
2021      51.3                    74.35                65.37

      Min Social Support    Max Social Support    Avg Social Support
2011
2021


---

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# Feeling adventurous?

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer.

- And if you want more bells and whistles, there is also `xaringanExtra`: https://pkg.garrickadenbuie.com/xaringanExtra.
